\documentclass{article}

% Internal ICML-workshop draft.

\usepackage{microtype}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{pgfplots}

\usetikzlibrary{arrows.meta,positioning}
\pgfplotsset{compat=1.18}
\newcommand{\idlekv}{\textsc{IdleKV}}
\newcommand{\bbase}{\ensuremath{B_{\mathrm{base}}}}
\newcommand{\bmatch}{\ensuremath{B_{\mathrm{match}}}}
\newcommand{\oraclek}{\ensuremath{\mathrm{Oracle}\mbox{-}K}}

\usepackage{icml2026}

\icmltitlerunning{IdleKV: Refreshing Stale KV Caches}

\begin{document}

\twocolumn[
  \icmltitle{IdleKV: Repairing Stale KV Caches Between Turns}

  \begin{icmlauthorlist}
    \icmlauthor{Shreyan Paliwal}{equal,harvard}
    \icmlauthor{Andrew Rusli}{equal,harvard}
  \end{icmlauthorlist}
  \icmlaffiliation{equal}{Equal contribution}
  \icmlaffiliation{harvard}{Harvard College, Cambridge, MA, USA}
  \icmlcorrespondingauthor{Shreyan Paliwal}{shreyanpaliwal@college.harvard.edu}
  \icmlkeywords{adaptive inference, KV cache repair, long-context agents,
    tool calling, runtime systems}
  \vskip 0.3in
]

\printAffiliationsAndNotice{\icmlEqualContribution}

\begin{abstract}
Tool-using agents create idle gaps between turns, but long-context
inference systems usually compress KV caches before the next turn is
known.
That can leave a stale active cache: tokens that looked unimportant at
turn $N$ may become critical once a follow-up query is revealed.
We study this as a matched-footprint adaptive-inference problem and
introduce \idlekv{}, a minimal idle-window mechanism that buffers evicted
KV on CPU, scores it against the now-known turn-$(N{+}1)$ query, and
restores up to $K$ context tokens before decoding resumes.
On a Qwen2.5-7B-Instruct prototype at 32K context, a calibrated
nonzero-baseline regime on a pooled split-query MQ-NIAH-4q suite keeps
matched no-repair performance near $0.10$, while \idlekv{} rises from
$0.342$ at $K=8$ to $0.685$ at $K=64$; random and oldest-token repairs
stay near baseline, and oracle repair reaches $1.0$ by $K=48$.
The prototype transfer-and-restore path stays below $50$\,ms p50 through
$K=500$ on the target hardware, suggesting that idle-window cache
maintenance is a practical and promising adaptive-inference primitive
for long-context agents.
\end{abstract}

% -----------------------------------------------------------------------
\section{Introduction}
% -----------------------------------------------------------------------

\paragraph{Motivation.}
Adaptive inference is increasingly shaped by deployment constraints, and
tool-using agents make that pressure especially clear.
In batch-1 settings, decoding is interleaved with file reads, tests,
retrieval, remote APIs, and other external actions that pause
generation for milliseconds to seconds.
Those pauses are usually treated as dead time.
We argue that they expose a valuable new adaptation point: the idle
interval between turns.
We study a specific cross-turn case: revising a compressed cache after
new turn information arrives but before decoding resumes.

\paragraph{Adjacent work.}
On the systems side, PagedAttention/vLLM improves KV-memory efficiency
during serving~\citep{vllm}, while InferCept preserves paused requests
to avoid recomputing prefixes when augmented generation
resumes~\citep{infercept}.
On the efficient-decoding side, SnapKV, StreamingLLM, and H$_2$O
compress the cache under a fixed budget, while query-aware methods such
as QUEST emphasize that token criticality depends on the
query~\citep{snapkv,streamingllm,h2o,quest}.
These methods address adjacent parts of the problem, but not the
cross-turn case studied here.
Serving systems preserve interrupted state efficiently, while
query-aware compression still chooses the active cache before the next
turn is known.
By contrast, \idlekv{} starts from an already compressed paused state,
does not rerun selection over the full prefix, and revises memory only
within the idle-window latency budget before decoding resumes.

\paragraph{Problem setting.}
For long-context agents, relevance over a fixed context can shift across
turns.
A tool result or follow-up question can make earlier context newly
important, and recent analysis shows that KV compression can sharply
degrade instructions and facts that later become
important~\citep{pitfalls}.
The core failure is therefore temporal: the cache is allocated using the
wrong relevance signal for the next turn.
In practical terms, the system keeps what looked important last turn
instead of what will matter once the tool call returns.
Current benchmarks also leave this regime under-specified.
Single-turn long-context tasks can show compression loss, and serving
benchmarks can show pause/resume efficiency, but neither isolates
whether future-turn information can improve a compressed cache at fixed
final active decode-time footprint.
A useful benchmark for this setting needs explicit turn boundaries, a
hidden future query, shared pre-turn history, and matched-footprint
controls.

\paragraph{Approach and scope.}
\idlekv{} targets this gap with dynamic KV cache repair.
After turn $N$, the runtime compresses the evictable context portion to a
base budget, buffers evicted KV on CPU, waits for the tool call, and
during the idle window scores the buffer against the now-known
turn-$(N{+}1)$ query before restoring up to $K$ context tokens.
The adaptation happens in the active KV allocation itself, not in model
depth, routing, or weight choice.
This is state-revising pre-resume repair: unlike pause/resume serving,
it intentionally mutates memory before resumption; unlike within-turn
query-aware compression, it starts from a paused compressed state and
does not rerun full-prefix selection once $Q_2$ is revealed.
The practical question is whether tool-call time can be used to improve
the \emph{final} cache seen by the next turn at the same final active
decode-time footprint.
Concretely, the paper contributes:
\begin{itemize}[leftmargin=1.4em,noitemsep,topsep=2pt]
  \item a matched-footprint protocol for cross-turn relevance shift that
  isolates better cache selection from simply keeping more tokens; and
  \item a calibrated nonzero-baseline result on a pooled split-query
  MQ-NIAH-4q suite where \idlekv{} substantially exceeds matched
  no-repair retention and simple restore controls; and
  \item a simple idle-window repair path with prototype latency
  measurements on one model, one eviction policy, and one hardware
  stack.
\end{itemize}
The paper still makes a narrow claim: one model, one eviction policy,
one synthetic task family, and one calibrated regime.

% -----------------------------------------------------------------------
\section{Protocol}
\label{sec:method}
% -----------------------------------------------------------------------

\paragraph{Overview.}
The key systems assumption is simple: a paused request need not preserve
its memory state exactly.
If the next turn is already known, the idle interval before resumption
can be used to improve the active cache that the next decode phase will
see.
We study the smallest such mechanism: repair buffered evictions without
rerunning a full query-aware compressor over the entire prefix.

\paragraph{Two-turn protocol.}
The protocol is simple.
The model first processes a long context and answers $Q_1$ from the full
cache.
After that answer, the runtime compresses only the evictable context
portion to a base budget $\bbase$, while preserving the exact $Q_1$
prompt and generated-answer tail.
During the subsequent tool-call idle window, the turn-$(N{+}1)$ query
$Q_2$ becomes known.
\idlekv{} encodes $Q_2$ against the active post-$Q_1$ cache, scores the
evicted context tokens against that signal, restores $K$ buffered
context tokens, and answers $Q_2$ from the repaired cache.
The protocol does not rerun full-prefix compression after $Q_2$ is
revealed.

\begin{figure}[t]
\centering
\begin{tikzpicture}[font=\small, >=latex,
  box/.style={draw, rounded corners=3pt, align=center,
              inner sep=3.5pt, minimum width=1.55cm},
  gpu/.style={box, fill=blue!8, draw=blue!60!black},
  cpu/.style={box, fill=orange!10, draw=orange!70!black}]
  \node[gpu] (turnn) at (0,0) {\textbf{Turn $N$}\\prefill + $Q_1$};
  \node[box, fill=gray!8] (idle) at (3.25,0) {\textbf{Tool call}\\idle window};
  \node[gpu] (turnn1) at (6.5,0) {\textbf{Turn $N{+}1$}\\answer $Q_2$};

  \node[cpu] (buf) at (1.7,-1.8) {CPU buffer\\evicted KV};
  \node[box, draw=gray, dashed] (score) at (4.85,-1.8) {score vs $Q_2$\\restore $K$ tokens};

  \draw[->, thick] (turnn) -- (idle);
  \draw[->, thick] (idle) -- (turnn1);
  \draw[->, dashed] (turnn.south) .. controls (0.5,-1.0) and (1.0,-1.3) .. (buf.north)
    node[midway, left, font=\tiny]{evict to $\bbase$};
  \draw[->] (buf.east) -- (score.west)
    node[midway, above, font=\tiny]{$Q_2$-aware scoring};
  \draw[->, dashed] (score.north) .. controls (5.45,-1.0) and (6.05,-0.5) .. (turnn1.south)
    node[midway, right, font=\tiny]{restore $K$};
\end{tikzpicture}
\caption{\idlekv{} uses the tool-call gap between turns to rescore
buffered KV and restore $K$ context tokens before answering $Q_2$.}
\label{fig:pipeline}
\end{figure}

\paragraph{Repair unit.}
Our prototype restores short query-scored local bursts rather than
isolated single tokens.
Here $K$ always denotes a restored-context-token budget, not an anchor
count.
Candidate anchor positions in the evicted buffer are ranked by the
future-query signal; accepted bursts are merged on overlap; and
restoration stops once $K$ context tokens have been reactivated.
For split-query retrieval tasks, this is the right unit of repair: the
query often contains a key-bearing anchor while the answer depends on
nearby value tokens.

\paragraph{Evaluation principle.}
All main claims are made against a no-repair baseline with the same
final active decode-time footprint.
Let $\bmatch$ denote the no-repair condition that applies the base
eviction policy with context budget $\bbase + K$ while preserving the
same $Q_1$ prompt and answer tail.
Because every compared run shares the same preserved tail and the same
active-token budget, the active cache footprint seen by $Q_2$ is
matched across $\bmatch$, \idlekv{}, and $\oraclek$, although the
selected context tokens differ by design.
Total retained CPU+GPU state is not matched, because \idlekv{} also
keeps an auxiliary CPU buffer of evicted KV.
We report:
\begin{equation}
  \mathrm{lift} =
  \mathrm{Score}(\mathrm{IdleKV}) - \mathrm{Score}(B_{\mathrm{match}})
\end{equation}
and
\begin{equation}
  \mathrm{recovery} =
  \frac{\mathrm{Score}(\mathrm{IdleKV})-\mathrm{Score}(B_{\mathrm{match}})}
       {\mathrm{Score}(\mathrm{Oracle}\mbox{-}K)-\mathrm{Score}(B_{\mathrm{match}})}.
\end{equation}
Here $\mathrm{Score}$ is the mean fraction of the two $Q_2$ needles
recovered correctly per example, averaged over the fixed evaluation set
shared across all conditions for that setting.
The numerator measures whether repair selects a better final cache than
matched no-repair retention; the denominator measures how much
recoverable headroom remains in the regime.
We report $\mathrm{recovery}$ only when
$\mathrm{Score}(\mathrm{Oracle}\mbox{-}K) >
\mathrm{Score}(B_{\mathrm{match}})$.
$\oraclek$ obeys the same $K$-token budget and the same burst-packing
rule as \idlekv{}, but ranks anchors using gold $Q_2$ needle locations
from the synthetic task metadata.
The protocol therefore tests whether newly revealed turn-$(N{+}1)$
information can improve a compressed cache relative to matched
no-repair retention.

% -----------------------------------------------------------------------
\section{Setup}
\label{sec:setup}
% -----------------------------------------------------------------------

\paragraph{Primary setting.}
The main text focuses on one primary benchmark slice rather than a broad
matrix.
We use Qwen2.5-7B-Instruct~\citep{qwen} at 32K rendered context on a
single RTX PRO 6000 Blackwell GPU, with SnapKV~\citep{snapkv} as the
base eviction policy.
The task family is a split-query version of \texttt{MQ-NIAH-4q} derived
from RULER~\citep{ruler}.
We treat three balanced $2|2$ set partitions as one pooled clean suite:
`14$\rightarrow$23', `24$\rightarrow$13', and `34$\rightarrow$12'.
These are the distinct balanced partitions whose $Q_2$ side excludes the
tail-anchored fourth needle, which would otherwise leak a recency freebie
into the no-repair baseline.
Within-turn order is not treated as a separate condition, so
`34$\rightarrow$12' and `43$\rightarrow$21' are equivalent up to prompt
permutation under the values-only scoring format.
Splits such as `12$\rightarrow$34' are left to diagnostics, because they
make the matched no-repair baseline easier for reasons unrelated to the
future-query mechanism.

\paragraph{Configuration.}
The main study avoids both recency-saturated settings and the all-zero
baseline regime found at much smaller budgets.
We therefore use context-only SnapKV with a fixed context recency
reserve and report the calibrated family-level regime:
\begin{itemize}[leftmargin=1.4em,noitemsep,topsep=2pt]
  \item context-only SnapKV with fixed recency reserve
  $R_{\mathrm{ctx}}=128$;
  \item base budget $\bbase=12288$;
  \item concise split prompts that request the values only,
  comma-separated, with a short answer prefix and fixed
  $24$-token decode budget per split turn;
  \item repair budgets $K \in \{8,16,32,48,64\}$ chosen by a small
  calibration sweep to keep the left edge non-dead and the right edge
  below oracle saturation; and
  \item one shared $Q_1$ transcript across all conditions and a fixed
  100-example evaluation set per split.
\end{itemize}
The turn-$N$ eviction signal is the exact generated $Q_1$ answer tail,
not a generic last-$32$-token cache suffix.

\paragraph{Condition semantics.}
We first generate one full-cache turn-$N$ transcript comprising the
shared context, $Q_1$, and the model-generated $Q_1$ answer tail.
Every condition reuses that exact transcript when answering $Q_2$.
$A$ keeps the full context active during $Q_2$ and is therefore the
full-cache ceiling under the fixed transcript.
$B$ compresses only the evictable context portion to $\bbase$.
$\bmatch$ applies the same base eviction policy at context budget
$\bbase + K$ and performs no repair.
Random-$K$ and Oldest-$K$ start from $B$ and restore the same $K$-token
budget from the same evicted buffer without future-query scoring.
\idlekv{} repairs $B$ during the idle gap, and $\oraclek$ applies the
same burst-packing rule using gold $Q_2$ needle locations from the
synthetic task metadata.

\paragraph{Scope.}
The paper keeps the main text to one task family, one model, and one
eviction policy.
That is enough to answer the first question cleanly: once the future
query is revealed, can idle-time repair produce a better final cache
than matched no-repair retention?
This study estimates conditional turn-$(N{+}1)$ quality given a fixed,
full-cache-generated turn-$N$ transcript; it does not measure end-to-end
two-turn agent quality.
The main benchmark slice is a positive-control suite chosen to keep
future relevance hidden, remove trivial recency wins from $Q_2$, and
keep eviction choices nontrivial, not to estimate average gains across
agent workloads.
It also does not yet compare against stronger learned or
future-query-aware alternative refresh mechanisms that use the same idle
window, or against a second task family calibrated to the same
acceptance rule.

% -----------------------------------------------------------------------
\section{Results}
\label{sec:results}
% -----------------------------------------------------------------------

\paragraph{Main matched-footprint result.}
Figure~\ref{fig:main-frontier} reports the pooled clean-suite frontier
for the completed main run at $\bbase=12288$.
In this calibrated nonzero-baseline regime, the compressed base score is
$0.093$ and the matched no-repair baseline stays near $0.10$ across the
entire $K$ sweep.
\idlekv{} rises from $0.342$ at $K=8$ to $0.685$ at $K=64$, while
Random-$K$ and Oldest-$K$ stay near $\bmatch$.
Oracle repair remains above \idlekv{} throughout, reaching $0.927$ at
$K=32$ and $1.0$ by $K=48$, so the regime still contains real headroom.
Selection lift over $\bmatch$ grows from $0.24$ at $K=8$ to $0.585$ at
$K=64$, and \idlekv{} exceeds $\bmatch$ on $92.3\%$ of examples at the
right edge of the sweep.

\begin{figure}[t]
  \centering
  \begin{tikzpicture}
    \begin{axis}[
      width=\columnwidth,
      height=0.68\columnwidth,
      xmin=8, xmax=64,
      ymin=0, ymax=1.05,
      xtick={8,16,32,48,64},
      xlabel={Restore budget $K$},
      ylabel={Mean turn-2 score},
      legend style={font=\scriptsize, at={(0.02,0.98)}, anchor=north west},
      grid=major,
      line width=0.9pt,
    ]
      \addplot[black, dashed] coordinates {(8,1.0) (64,1.0)};
      \addlegendentry{$A$}
      \addplot[gray!70!black, mark=square*] table [x=k, y=b_match, col sep=comma] {figures/phase6_clean_suite_b12288_overall.csv};
      \addlegendentry{$B_{\mathrm{match}}$}
      \addplot[blue!70!black, mark=*] table [x=k, y=idlekv, col sep=comma] {figures/phase6_clean_suite_b12288_overall.csv};
      \addlegendentry{\idlekv{}}
      \addplot[teal!70!black, mark=triangle*] table [x=k, y=random_k, col sep=comma] {figures/phase6_clean_suite_b12288_overall.csv};
      \addlegendentry{Random-$K$}
      \addplot[orange!90!black, mark=diamond*] table [x=k, y=oldest_k, col sep=comma] {figures/phase6_clean_suite_b12288_overall.csv};
      \addlegendentry{Oldest-$K$}
      \addplot[red!75!black, mark=otimes*] table [x=k, y=oracle_k, col sep=comma] {figures/phase6_clean_suite_b12288_overall.csv};
      \addlegendentry{\oraclek{}}
    \end{axis}
  \end{tikzpicture}
  \caption{Pooled clean-suite frontier at $\bbase=12288$.
  Matched no-repair retention stays near $0.10$, simple restore controls
  remain near baseline, and \idlekv{} approaches the oracle curve as
  $K$ grows.}
  \label{fig:main-frontier}
\end{figure}

\paragraph{Split heterogeneity.}
The pooled result hides a real spread in difficulty across the three
clean splits.
Table~\ref{tab:split-endpoints} shows the right edge of the frontier.
`14$\rightarrow$23' is easy once repair has enough budget, and
`24$\rightarrow$13' is moderate.
`34$\rightarrow$12' is the hard split: both $B$ and $\bmatch$ stay at
zero there, but oracle repair still reaches $1.0$, which indicates that
the benchmark is valid while the current selector leaves substantial
headroom on the hardest slice.

\begin{table}[t]
  \caption{Per-split frontier endpoints at $K=64$.}
  \label{tab:split-endpoints}
  \centering
  \small
  \setlength{\tabcolsep}{4pt}
  \begin{tabular}{l c c c c}
    \toprule
    split & $B$ & $\bmatch$ & \idlekv{} & \oraclek{} \\
    \midrule
    $14 \rightarrow 23$ & 0.160 & 0.175 & 1.000 & 1.000 \\
    $24 \rightarrow 13$ & 0.120 & 0.125 & 0.540 & 1.000 \\
    $34 \rightarrow 12$ & 0.000 & 0.000 & 0.515 & 1.000 \\
    \bottomrule
  \end{tabular}
\end{table}

\paragraph{Measured feasibility.}
Table~\ref{tab:latency} reports the current measured overheads on the
target hardware for the prototype repair path.

\begin{table}[t]
  \caption{Measured repair overhead on the target hardware.}
  \label{tab:latency}
  \centering
  \small
  \setlength{\tabcolsep}{4pt}
  \begin{tabular}{l c c c}
    \toprule
    $K$ & transfer p50 & total repair p50 & total repair p99 \\
    \midrule
    100 & 2.68\,ms  & 35.00\,ms & 37.34\,ms \\
    250 & 6.09\,ms  & 38.89\,ms & 40.44\,ms \\
    500 & 12.58\,ms & 46.94\,ms & 53.47\,ms \\
    \bottomrule
  \end{tabular}
\end{table}

Measured transfer-plus-restore p50 stays below 50\,ms through $K=500$.
On the main quality run, the restore-only part of \idlekv{} averages
$22.2$\,ms at $K=8$ and about $17$--$18$\,ms from $K=16$ through
$K=64$, while the exact CPU-side evicted-pool scoring pass averages
about $226$\,ms per example.
The prototype is therefore still scoring-dominated rather than
transfer-dominated, but the end-to-end overhead remains small relative
to many real tool-call delays.

% -----------------------------------------------------------------------
\section{Discussion}
\label{sec:discussion}
% -----------------------------------------------------------------------

\paragraph{Position in adaptive inference.}
This paper is best read as a runtime-systems and benchmarking
contribution for adaptive inference.
Within that landscape, flexible architectures and routing change the
model path; test-time compute changes how much computation to spend;
compression and optimization reduce model or token cost; and efficient
decoding adapts attention or cache retention within a turn.
\idlekv{} points to a complementary question: once a request is paused
and compressed, can the runtime use the idle gap to revise memory before
the next turn begins?
That question matters most for agent workloads, because external actions
create exactly the pause in which such revision can happen.

\paragraph{Relation to serving systems.}
\idlekv{} is complementary to serving systems such as vLLM and
InferCept.
Those systems decide how to preserve, schedule, and resume interrupted
requests efficiently~\citep{vllm,infercept}; \idlekv{} asks what useful
quality-improving work can be done \emph{during} the interruption before
decoding resumes.
It is therefore state-revising pre-resume repair, not state-preserving
pause/resume serving.
It is also distinct from within-turn query-aware eviction: the request
has already been compressed, full-prefix recomputation is disallowed,
and the runtime operates under an idle-window latency budget.

\paragraph{When repair should help.}
Repair should help when new turn information changes relevance, the base
eviction policy still has real choice beyond recency, and the hindsight
ceiling leaves nontrivial headroom over $\bmatch$.
It should help less when the future turn adds little new information,
the keep budget is recency-saturated, or the idle gap is shorter than
the repair overhead.
These criteria matter both for benchmark design and for interpreting
null results.

\paragraph{Limitations and next steps.}
The study is intentionally conditional and favorable: one model, one
eviction policy, one synthetic split-query family, fixed
full-cache-generated turn-$N$ transcripts, and no stronger learned or
future-query-aware alternative post-$Q_2$ refresh baselines yet.
That makes the mechanism legible, but it is not evidence about
end-to-end two-turn agent quality or average gains across workloads.
The current selector is also still leaving clear headroom on the harder
clean splits.
In this prototype, ``improving the selector'' means better choosing
which evicted bursts to reactivate once $Q_2$ is known: for example,
adaptive burst widths, stronger scoring of value-bearing neighbors,
active-cache-aware marginal gain estimates, or multi-anchor packing
rules that avoid spending budget on partially redundant restorations.
The immediate next steps are therefore broader evidence on additional
families calibrated to the same acceptance rule, explicit diagnostic
tail-leaky splits such as $12\rightarrow34$, and stronger post-$Q_2$
selection policies on the existing benchmark before moving to noisier
agent-style tasks.
One preflight caveat is that a task-matched mismatched-query control did
not separate reliably on this templated NIAH family, likely because even
wrong queries recover generic key/value bursts; we therefore emphasize
matched-footprint and simple-restore controls in the main text and treat
wrong-query controls as a benchmark-design issue to revisit on broader
tasks.
More broadly, the field still needs benchmarks with explicit idle
intervals, hidden future queries, matched no-repair controls, hindsight
ceilings, and latency measurements tied to real interruption windows.
If those studies continue to show gains, then idle-window memory
maintenance becomes a plausible systems primitive for long-context
agents.

% -----------------------------------------------------------------------
\section{Conclusion}
\label{sec:conclusion}
% -----------------------------------------------------------------------

Tool-call stalls in agent workflows can be treated as part of the
inference budget rather than as dead time.
\idlekv{} contributes a concrete way to spend that budget: revise a
compressed cache before the next turn under a matched final active
decode-time footprint.
On the primary pooled split-query benchmark, the completed main run
shows that idle-window repair can substantially outperform matched
no-repair retention while random and oldest-token restores stay near
baseline.
The remaining work is to broaden that evidence across families and to
close the gap between the current selector and the available oracle
headroom.
More broadly, long-context agent systems may need to be judged not only
by how efficiently they decode, but by how well they maintain memory
between turns.

% -----------------------------------------------------------------------
\begin{thebibliography}{10}

\bibitem[Abhyankar et~al.(2024)]{infercept}
Abhyankar, R., He, Z., Srivatsa, V., Zhang, H., and Zhang, Y.
\newblock InferCept: Efficient intercept support for augmented large
  language model inference.
\newblock In \emph{Proceedings of the 41st International Conference on
  Machine Learning (ICML)}, 2024.

\bibitem[Hsieh et~al.(2024)]{ruler}
Hsieh, C.-Y., Sun, S., Kriman, S., Acharya, S., Rekesh, D., Jia, F.,
  Zhang, Y., and Ginsburg, B.
\newblock RULER: What's the real context window size of your LLM?
\newblock \emph{arXiv:2404.06654}, 2024.

\bibitem[Kwon et~al.(2023)]{vllm}
Kwon, W., Li, Z., Zhuang, S., Sheng, Y., Zheng, L., Yu, C. H.,
  Gonzalez, J. E., Zhang, H., and Stoica, I.
\newblock Efficient memory management for large language model serving
  with PagedAttention.
\newblock In \emph{Proceedings of the 29th ACM Symposium on Operating
  Systems Principles (SOSP)}, 2023.

\bibitem[Li et~al.(2024)]{snapkv}
Li, Y., Huang, Y., Yang, B., Venkitesh, B., Locatelli, A., Ye, H.,
  Cai, T., Lewis, P., and Chen, D.
\newblock SnapKV: LLM knows what you are looking for before generation.
\newblock \emph{arXiv:2404.14469}, 2024.

\bibitem[Chen et~al.(2025)]{pitfalls}
Chen, A., Geh, R., Grover, A., Van den Broeck, G., and Israel, D.
\newblock The pitfalls of KV cache compression.
\newblock \emph{arXiv:2510.00231}, 2025.

\bibitem[Qwen(2024)]{qwen}
Qwen Team.
\newblock Qwen2.5 technical report.
\newblock \emph{arXiv:2412.15115}, 2024.

\bibitem[Tang et~al.(2024)]{quest}
Tang, J., Zhao, Y., Zhu, K., Xiao, G., Kasikci, B., and Han, S.
\newblock QUEST: Query-aware sparsity for efficient long-context LLM
  inference.
\newblock In \emph{Proceedings of the 41st International Conference on
  Machine Learning (ICML)}, 2024.

\bibitem[Xiao et~al.(2024)]{streamingllm}
Xiao, G., Tang, Y., Zuo, J., Guo, J., Yang, S., Tang, H., Fu, Y.,
  and Han, S.
\newblock Efficient streaming language models with attention sinks.
\newblock In \emph{International Conference on Learning Representations
  (ICLR)}, 2024.

\bibitem[Zhang et~al.(2023)]{h2o}
Zhang, Z., Sheng, Y., Zhou, T., Chen, T., Zheng, L., Cai, R., Song, Z.,
  Tian, Y., R{\'e}, C., Barrett, C., Wang, Z., and Chen, B.
\newblock H$_2$O: Heavy-hitter oracle for efficient generative inference
  of large language models.
\newblock In \emph{Advances in Neural Information Processing Systems
  (NeurIPS)}, 2023.

\end{thebibliography}

\end{document}
